Introduction to Markov state modeling with the PyEMMA software --- v\versionnumber

### 2018-09-03 manuscript/manuscript.tex
minor changes, review beh

A case in point is the curse of dimensionality:
it is hard to discretize a high dimensional feature space, not only because it is computationally demanding.
More important, Euclidean distances become less meaningful with increasing dimensionality~\cite{aggarwal_surprising_2001} and, thus, cluster assignment based on that norm are prone to yield poor discretizations.
Especially for large systems, it is thus particularly important for first find a suitable set of features, and to further apply dimension reduction techniques (e.g. TICA, VAMP, if applicable) to obtain a low-dimensional representation of the slow dynamics.
Hidden Markov models might further mitigate poor discretization to a certain extend~\cite{noe-proj-hid-msm}.

In addition, the slowest process in a system as identified by an MSM or HMM might not be the one a modeler is interested in.
For instance, the slowest process might correspond to a biologically irrelevant side chain flip that only occurred once in the data set.
This problem can often be mitigated by choosing a more specific set of features.

The technical challenges with large systems are usually high demands in memory and computation time; we explain how to deal with those in the tutorials.

More details on how to model complex systems with the techniques presented here are described e.g. by~\cite{plattner_protein_2015,plattner_complete_2017}.

>>>>

A case in point is the curse of dimensionality:~it is difficult to discretize a high dimensional feature space. While it is somewhat computationally demanding, more importantly, Euclidean distances become less meaningful with increasing dimensionality~\cite{aggarwal_surprising_2001} and thus cluster assignments based on that norm may yield a poor discretization.
Especially for large systems, it is thus particularly important to first find a suitable set of features, and to further apply dimensionality reduction techniques (e.g.~TICA, VAMP, if applicable) to obtain a low dimensional representation of the slow dynamics.
Hidden Markov models (HMMs) might further mitigate poor discretization to a certain extent~\cite{noe-proj-hid-msm}.

Furthermore, the slowest process in a system as identified by an MSM or HMM might not be the one a modeler is interested in~\cite{banushkina_nonparametric_2015}.
For instance, the slowest process might correspond to a biologically irrelevant side chain flip that only occurred once in the data set.
This problem may be mitigated by choosing a more specific set of features.

Additional technical challenges for large systems include high demands on memory and computation time; we explain how to deal with those in the tutorials.

More details on how to model complex systems with the techniques presented here are described e.g.~by~\cite{plattner_protein_2015,plattner_complete_2017}.
